Effect of Earnings and Dividends on Stock Prices

### 2024-04-12 outputs/paper/paper.qmd
paper updates

---
title: "Effect of Earnings and Dividends on Stock Prices"
subtitle: "Analysis of the Relationship Between Stock Price, Earnings Per Share, and Dividends of the Largest 50 North American Companies from 2013 to 2023"
author: Diana Liu
thanks: "Code and data are available at: https://github.com/Diana-Guanzhi-Liu/Relationship-Between-Stock-Prices-and-Common-Financial-Metrics"
date: today
date-format: long
abstract: "This study examines the relationship between Earnings per Share (EPS), dividends, and stock prices in publicly traded companies. Findings indicate a positive correlation between EPS and stock price, with each dollar increase in EPS associated with a $26.59 rise in stock price. Conversely, dividend payments are linked to a decrease in stock price, mitigating the impact of EPS on price. These insights enable investors to predict stock prices, informing their investment strategies, as well as guide managerial decisions balancing pleasing existing shareholders by paying dividends, ensuring long-term growth of the company, and keeping the stock attractive to new investors."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Effect of Earnings and Dividends on Stock Prices"
subtitle: "Analysis of the Relationship Between Stock Price, Earnings Per Share, and Dividends of the Largest 50 North American Companies from 2013 to 2023"
author: Diana Liu
thanks: "Code and data are available at: https://github.com/Diana-Guanzhi-Liu/Effect-of-Earnings-and-Dividends-on-StockPrices"
date: today
date-format: long
abstract: "This study examines the relationship between Earnings per Share (EPS), dividends, and stock prices in publicly traded companies. Findings indicate a positive correlation between EPS and stock price, with each dollar increase in EPS associated with a $26.59 rise in stock price. Conversely, dividend payments are linked to a decrease in stock price, mitigating the impact of EPS on price. These insights enable investors to predict stock prices, informing their investment strategies, as well as guide managerial decisions balancing pleasing existing shareholders by paying dividends, ensuring long-term growth of the company, and keeping the stock attractive to new investors."
format: pdf
number-sections: true
bibliography: references.bib
---
